---
title: "Developing Data Products"
subtitle: "Week 4 Assignment"
author: "JingYi"
date: "12/8/2019"
output: ioslides_presentation
---

<style type="text/css">

body, td {
   font-size: 14px;
}
code.r{
  font-size: 12px;
}
pre {
  font-size: 12px
}
</style>

## Introduction

This project part of the Course Project for the Coursera Developing Data Products course. The objective of this project is to create a Shiny application and deploy it on Rstudio's servers. 

The app develop for the first part of the project is available at:

https://jingy1.shinyapps.io/COURSE9_PROJ3/

The source code for ui.R and server.R is available at:

https://github.com/JINGY1/Developing_Data_Products_Proj3


## Data

Datasets **nottem** is used to predict average monthly temperature at Nottingham. *nottem* is a time series object containing average air temperatures at Nottingham Castle in degrees Fahrenheit for 20 years.


## Data

```{r data, echo=TRUE, message=FALSE}
options(width = 80)
summary(nottem)
str(nottem)
head(nottem, 20)
```


## Analysis
In this project, we are going to use the 20 years data to predict next 10 years air temperature.
```{r plot, include=TRUE, out.width='80%', fig.align='center'}
plot(nottem)
```


